\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-06-07 doc/USER_MANUAL/02_getting_started.tex
clarified the "configure" command

Then, to configure the software for your system, run the \texttt{configure}
shell script. This script will attempt to guess the appropriate configuration
values for your system. However, at a minimum, it is recommended that
you explicitly specify the appropriate command names for your Fortran
compiler and MPI package (another option is to define FC, CC and MPIF90
in your .bash\_profile or your .cshrc file):
\begin{verbatim}
./configure FC=ifort MPIFC=mpif90
\end{verbatim}
\noindent
Note that MPI must be installed with MPI-IO enabled because parts of SPECFEM3D perform I/Os through MPI-IO.

@@

>>>>

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran compiler (another option is to define FC, CC and MPIF90 in your .bash\_profile
or your .cshrc file):
%
\begin{verbatim}
    ./configure FC=gfortran CC=gcc
\end{verbatim}
%
If you want to run in parallel, i.e., using more than one processor core, then you would type
%
\begin{verbatim}
    ./configure FC=gfortran CC=gcc MPIFC=mpif90 --with-mpi
\end{verbatim}

You can replace the GNU compilers above (gfortran and gcc) with other compilers if you want to; for instance for Intel ifort and icc use FC=ifort CC=icc instead.

Note that MPI must be installed with MPI-IO enabled because parts of SPECFEM3D perform I/Os through MPI-IO.

@@

To visualize the call tree (calling tree) of the source code, you can see the Doxygen tool available in directory \texttt{doc/call\_trees\_of\_the\_source\_code}.
